---
title: "ForestHerNC_MPAnalysis"
author: "Emma Childs"
date: "2024-01-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r loading packages, include=FALSE, warning=FALSE, message=FALSE}

rm(list=ls())
library(ggplot2)
library(tidyr)
library(tidyverse)
library(plm)
library(GGally)
library(car)
library(lmtest)
library(sandwich)
library(gt)
library(ggrepel)
library(tinytex)
#installing and loading necessary packages
#tinytex::install_tinytex() when first starting to be able to knit into spiffy looking PDFs if necessary. 
```


##Reading in original data and cleaning

```{r working directory, include=FALSE, warning=FALSE, message=FALSE}

#setwd("C:/Users/EmmaC/Documents/Duke_Academics/Fall_2023_Classes/MASTERS_PROJECT/R_Coding/FHNC_Rcode")
#don't need this code chunk bc I set up a R Project folder that renders this unnecessary. 
```


```{r reading in original FHNC survey data, include=FALSE, warning=FALSE, message=FALSE}

FHNC23.df<-read_csv("ORIGINAL_ForestHerNC_2023Implementation_Survey.csv") %>%
  glimpse()

FHNC23.df
#reading in CSV files for 2023 ForestHer NC end of year implementation survey. 
``` 


```{r correcting Qualtrics formatting}

FHNC23.data.df <- read_csv("ORIGINAL_ForestHerNC_2023Implementation_Survey.csv", 
    col_names = FALSE, skip = 3)
#reading in only data

FHNC23.Qs.df <- read_csv("ORIGINAL_ForestHerNC_2023Implementation_Survey.csv", 
    n_max = 1)
#reading in Qualtrics questions that get embedded in CSV file that we may want to use later.

my_colnames_vec <- colnames(FHNC23.Qs.df)

colnames(FHNC23.data.df) <- my_colnames_vec
```


```{r initial column cleaning}

FHNC23.clean.df <- FHNC23.data.df %>% 
  select(Progress, ResponseId, Q2:Q23)
#Eliminated several superfluous columns with information that was not needed for analysis (start time, end time, etc.) to make everything cleaner. Be sure to keep the Response ID so you have an identifier for each response. 
```


```{r cleaning for higher completion survey rates, eval=FALSE}

FHNC23.clean.df <- FHNC23.clean.df %>%
  filter(Progress > 20)
#Could come back and make this threshold higher depending on what I'm looking for. Do I want to select or filter for the threshold? Then I can just filter out NAs???
```

#Subsetting main FHNC data to anlalyze on-the-ground management activities related to Q6.

```{r subset Q6 into separate df}

q6_df <- FHNC23.clean.df %>% 
  select(Progress, ResponseId, starts_with("Q6")) %>% 
  filter(Progress > 20)  %>% 
  janitor::clean_names()

#Creating a separate dataframe just for Q6 so I can analyze management actions. Filtering for responses more than 20% at the moment, but might change this. 
```


```{r glimpse Q6}

q6_df %>% 
  glimpse()
#glimpsing just to make sure I have all the data I want in this new subsetted dataframe. 
```


```{r}

library(readxl)
#Import theme data from Excel file from FHNC that has pivot table and all Q6 questions. First, do one-time install for the {readsxl} package to import the data; then load the {readxl} package
```


```{r reading in pivot excel table}

pivot_df <- read_excel("ImplementationSurveyAggregation_fromDakota_Feb2024.xlsx", sheet = "PivotTable")
pivot_df %>%  
  janitor::clean_names() %>% 
  drop_na(row_labels)
#Now import the excel file. I'll import both the pivot table from the first workbook sheet, and the 2021 data from the 2028 workbook sheet in the next code chunk. The Q6 questions are the same from years 2021-2023, so I can just read in the one 2021 sheet to keep things clean. 
```


```{r reading in excel 2021 sheet}

theme_2021 <- read_excel("ImplementationSurveyAggregation_fromDakota_Feb2024.xlsx", 
    sheet = "2021") %>%  
  janitor::clean_names() 
theme_2021 
#reading in 2021 sheet with all the specific forestry activities listed.
```


```{r}
theme_2021 |> 
  count(theme_1, sort = TRUE)
#Verify Theme 1 from raw data
```


```{r}
theme_2021 |> 
  count(theme_2, sort = TRUE)
#Verify theme 2 from raw data
```


```{r import pivot table csv}

#once imported, can do a left join with management activity and themes (see below code) - EMMA, come back here and clarify - this is from meeting with John Little on 3/19/2024
```


```{r group by mgmt activity}

#Direct vs indirect management - theme 2

#See Dakota's pivot table for further designations 

```


```{r group by topical theme}

#theme 1:
#education
#business management
#wildlife
#invasive species
#recreation
#timber/trees
#fire

```


```{r group by average parcel size}

#Filter by region and by parcel size to assess who owns land where, and how much

```


```{r FHNC analyses}

#consult list of planned analyses - what else do I need to include?

```

##Cooperative management data analysis

```{r subset cooperative data}

FHNC23.coop.df <- FHNC23.clean.df %>% 
  select(Progress, ResponseId, Q5, Q8_1:Q12, Q16:Q19) %>%
  filter(Progress > 80) 
#Selecting columns of interest, cooperative mgmt specific questions
```


```{r visualizing cooperative data Q8}

question_8_text <- FHNC23.Qs.df %>% 
  select(IPAddress, starts_with("Q8_")) %>% 
  pivot_longer(-IPAddress, names_to = "question", values_to = "question_text") %>% 
  mutate(question_short = str_remove(question_text, "Please select your level of interest in each of the following different services that cooperative forest management can offer. - Coordinating with adjacent landowners (on|to) ")) %>% 
  pull(question_short)
question_8_text
  
my_levels_8 <- c("Not Interested", "Not Sure", "Somewhat Interested", "Very Interested")
# my_levels_8 <- rev(c("Not Interested", "Not Sure", "Somewhat Interested", "Very Interested"))

# glimpse()
question_8_df <- FHNC23.coop.df %>% 
  select(ResponseId, starts_with("Q8_")) %>% 
  pivot_longer(-ResponseId, names_to = "question", values_to = "response") %>% 
  count(question, response) # %>% 
  # mutate(response = factor(response, levels = my_levels_8)) 

question_8_df
  # filter(Progress == 100) %>%
  # mutate(question = if_else(question == "Q8_1", "special", question))
  # mutate(question = case_when(
  #   question == "Q8_1" ~ "special-thing1",
  #   question == "Q8_2" ~ "special-thing2",
  #   TRUE ~ "foo"
  # ))
  # drop_na(response)
  # arrange(response, desc(n))
#Code we were just playing around with, but do not need at the moment - 4/3/24

question_8_df %>% 
  ggplot(aes(x = question, y = n)) +
  geom_col(aes(fill = response)) 

# question_8_df %>% 
#   ggplot(aes(x = question, y = n)) +
#   geom_col(aes(fill = response)) +
#   facet_wrap(vars(question))

#Visualizing question 8 - coordinating services with other landowners - still need to make the visualization more nuanced. 
```


##Q8 facet wrap to analyze different variables responding to Q8 - acreage owned, region of the state, etc. 

```{r Q8 and acreage visualization}

Q8_acreage_df <- FHNC23.coop.df %>% 
  select(ResponseId, starts_with("Q8_"), Q18) %>% 
  pivot_longer(-c(ResponseId, Q18), names_to = "question", values_to = "response") %>% 
  count(question, Q18, response) %>% 
  drop_na(Q18)

Q8_acreage_df
#pivoted longer here to include Q18 alongside Q8 inquiries. Q18 is how much acreage landowners have, starting from 1-20 acres and increasing from there. We dropped NAs from Q18 because those are folks who do not own land. This does leave out folks who might manage land, but it was the best option for this analysis. 
```


```{r Q8 acreage facet wrap}

Q8_acreage_df %>% 
  #filter(Q18 == "20 acres or less") %>% 
  ggplot(aes(x = question, y = n)) +
  geom_col(aes(fill = response)) +
  facet_wrap(vars(Q18)) #, scales = "free_y")
#Facet wrapped here so I Can see all the different acreage categories that FHNC asks about - 20 acres or less, 21-50 acres, 51-200 acres, or more than 200 acres. I've commented out the filter function which would allow me to look at just one acreage category at a time. My geom_col has the color of the bars filled in by response which are generated from the Likert scale. I've also commented out scales = "free_y" because that allows the y-axis to be unique for each plot, which is pretty confusing and conflates data provided by just a few participants. 
```


```{r Q8 and region visualization}

Q8_region_df <- FHNC23.coop.df %>% 
  select(ResponseId, starts_with("Q8_"), Q16) %>% 
  pivot_longer(-c(ResponseId, Q16), names_to = "question", values_to = "response") %>% 
  count(question, Q16, response) 
  #drop_na(Q16)

Q8_region_df
#COME BACK AND FINISH THIS ONE, EMMA - plus the facet wrap for visualizing...do I want to drop the NAs or not? Currently it is commented out...
```


```{r Q8 region facet wrap}

Q8_region_df %>% 
  filter(Q16 == "Coastal", "Mountains", "Piedmont") %>% 
  ggplot(aes(x = question, y = n)) +
  geom_col(aes(fill = response)) +
  facet_wrap(vars(Q16)) #, scales = "free_y")}
#Error here - why??? Trying to filter for just the three main regions...
```


```{r visualizing cooperative data Q9}

question_9_text <- FHNC23.Qs.df %>% 
  select(IPAddress, starts_with("Q9_")) %>% 
  pivot_longer(-IPAddress, names_to = "question", values_to = "question_text") %>% 
  mutate(question_short = str_remove(question_text, "Please select the level of importance or unimportance for each of the following different benefits that cooperative forest management can offer. - ")) %>% 
  pull(question_short)
question_9_text
  
my_levels_9 <- c("Not Important", "Not Sure", "Somewhat Important", "Very Important")
# my_levels_9 <- rev(c("Not Important", "Not Sure", "Somewhat Important", "Very Inmportant"))

# glimpse()
question_9_df <- FHNC23.coop.df %>% 
  select(ResponseId, starts_with("Q9_")) %>% 
  select(!Q9_11_TEXT) %>% #using the bang ! here to signal that I don't want to include Q9_11_TEXT in my visualiz/results
  select(!Q9_11) %>% 
  pivot_longer(-ResponseId, names_to = "question", values_to = "response") %>% 
  count(question, response) # %>% 
  # mutate(response = factor(response, levels = my_levels_9)) 

question_9_df
  # filter(Progress == 100) %>%
  # mutate(question = if_else(question == "Q9_1", "special", question))
  # mutate(question = case_when(
  #   question == "Q9_1" ~ "special-thing1",
  #   question == "Q9_2" ~ "special-thing2",
  #   TRUE ~ "foo"
  # ))
  # drop_na(response)
  # arrange(response, desc(n))

question_9_df %>% 
  ggplot(aes(x = question, y = n)) +
  geom_col(aes(fill = response)) 

#Visualizing question 9 - potential different benefits that coordinated services could offer. 

```


```{r visualizing cooperative data Q10}

question_10_text <- FHNC23.Qs.df %>% 
  select(IPAddress, starts_with("Q10_")) %>% 
  pivot_longer(-IPAddress, names_to = "question", values_to = "question_text") %>% 
  mutate(question_short = str_remove(question_text, "Please select the level of significance or insignificance for each of the following different barriers to engaging in cooperative forest management for you and your land. - ")) %>% 
  pull(question_short)
question_10_text
  
my_levels_10 <- c("Not Significant", "Not Sure", "Somewhat Significant", "Very Significant")
# my_levels_10 <- rev(c("Not Significant", "Not Sure", "Somewhat Significant", "Very Significant"))

# glimpse()
question_10_df <- FHNC23.coop.df %>% 
  select(ResponseId, starts_with("Q10_")) %>%
  select(!Q10_9_TEXT) %>% 
  select(!Q10_9) %>% 

  pivot_longer(-ResponseId, names_to = "question", values_to = "response") %>% 
  count(question, response) # %>% 
  # mutate(response = factor(response, levels = my_levels_10)) 

question_10_df
  # filter(Progress == 100) %>%
  # mutate(question = if_else(question == "Q10_1", "special", question))
  # mutate(question = case_when(
  #   question == "Q10_1" ~ "special-thing1",
  #   question == "Q10_2" ~ "special-thing2",
  #   TRUE ~ "foo"
  # ))
  # drop_na(response)
  # arrange(response, desc(n))

question_10_df %>% 
  ggplot(aes(x = question, y = n)) +
  geom_col(aes(fill = response))

#Visualizing question 10 - the level of significance or insignificance for each of the following different barriers to engaging in cooperative forest management for you and your land.


```


```{r visualizing cooperative data Q11}

question_11_text <- FHNC23.Qs.df %>% 
  select(IPAddress, starts_with("Q11_")) %>% 
  pivot_longer(-IPAddress, names_to = "question", values_to = "question_text") %>% 
  mutate(question_short = str_remove(question_text, "To what degree would each of the following allow you to engage in cooperative forest management? - ")) %>% 
  pull(question_short)
question_11_text
  
my_levels_11 <- c("Not at all", "Not Sure", "Somewhat", "Greatly")
# my_levels_11 <- rev(c("Not at all", "Not Sure", "Somewhat", "Greatly"))

# glimpse()
question_11_df <- FHNC23.coop.df %>% 
  select(ResponseId, starts_with("Q11_")) %>% 
  select(!Q11_7_TEXT) %>% 
  select(!Q11_7) %>% 
  pivot_longer(-ResponseId, names_to = "question", values_to = "response") %>% 
  count(question, response) # %>% 
  # mutate(response = factor(response, levels = my_levels_11)) 

question_11_df
  # filter(Progress == 100) %>%
  # mutate(question = if_else(question == "Q11_1", "special", question))
  # mutate(question = case_when(
  #   question == "Q11_1" ~ "special-thing1",
  #   question == "Q11_2" ~ "special-thing2",
  #   TRUE ~ "foo"
  # ))
  # drop_na(response)
  # arrange(response, desc(n))

question_11_df %>% 
  ggplot(aes(x = question, y = n)) +
  geom_col(aes(fill = response)) 

# question_11_df %>% 
#   ggplot(aes(x = question, y = n)) +
#   geom_col(aes(fill = response)) +
#   facet_wrap(vars(question))

#Visualizing question 11 - To what degree would each of the following allow you to engage in cooperative forest management?

```


```{r recode cooperative Qs to numeric}

#Qs 8-11 (12 also is a coop Q but character response) - need to match USFS coding - add column for 1-5 values?
```


```{r test run analyses}

#barchart/histogram by response type (1-5)?...and then could do a further visualization by region? Or could run more statistical analyses. 

```

# Go through each question and figure out what value I want or need from that Q for analysis. (Prioritize the columns I know that I want, and then work backyards.)

#Start recoding Likert cooperative Qs to be numeric - can use recode() or other code Lauren sent - use same numeric values that USFS uses that Jesse sent
